Modelling the Lymphatic Metastatic Progression Pathways of OPSCC \\ from Multi-Institutional Datasets

### 2024-02-05 src/tex/ms.tex
[showyourwork] overleaf sync

Lastly, the \LaTeX\ source code, all Python scripts to generate the figures and tables in this work, and the pipeline definition to build the document (using \showyourwork) are made public in the GitHub repository \href{https://github.com/rmnldwg/graph-extension-paper}{\texttt{rmnldwg/graph-extension-paper}}. To rebuild it, the \showyourwork tool pulls the patient data from the \href{https://github.com/rmnldwg/lynference}{\texttt{rmnldwg/lynference}} repository and the trained models in the form of \gls{mcmc} samples from the Azure blob storage container, then runs the Python scripts and compiles the \LaTeX\ article.

>>>>

Lastly, the \LaTeX\ source code, all Python scripts to generate the figures and tables in this work, and the pipeline definition to build the document (using \showyourwork \cite{luger_mapping_2021}) are made public in the GitHub repository \href{https://github.com/rmnldwg/graph-extension-paper}{\texttt{rmnldwg/graph-extension-paper}}. To rebuild it, the \showyourwork tool pulls the patient data from the \href{https://github.com/rmnldwg/lynference}{\texttt{rmnldwg/lynference}} repository and the trained models in the form of \gls{mcmc} samples from the Azure blob storage container, then runs the Python scripts and compiles the \LaTeX\ article.
